The large scale clustering in dispersion measure space

### 2015-05-14 writeup/dm_space_distortions.tex
Some text.

\renewcommand{\section}[1]{\emph{#1}---\ignorespaces}
\renewcommand{\subsection}[1]{}

@@

    The recently discovered fast radio bursts are a new class of radio
    transient that, due to their high dispersion from intervening plasma,
    have been interpreted as
    originating from cosmological distances.  The rate of fast radio bursts
    has been estimated to be as high as 10\,000 per sky per day.  If
    cosmological, these events should trace the large-scale structure of the
    Universe in some way. Furthermore, because the dispersion measure (DM) can be
    used as a proxy for radial distance (like redshift),
    clustering can be studied in three dimensions. Due to inhomogeneities in
    the plasma's density dispersion measure is an imperfect proxy or radial
    distance and we show that this leads to additional clustering terms---the
    dispersion measure space distortions. We calculate the DM space
    power spectra for a toy model of electron and FRB clustering and show that
    the clustering signal could be detected in a survey of $10^4$ FRB
    events, as is expected to be produced by the Canadian Hydrogen Intensity
    Mapping Experiment.

@@

\section{Introduction}
The clustering of matter on large scales has been
heralded as the next great probe the Universe after the cosmic microwave
background (CMB). The large-scale structure in principle contains far more
information than the CMB, because it can be studied in three dimensions.
Traditionally the redshift of spectral lines caused by the Hubble flow has
been employed to measure position in the radial direction. Such redshift
surveys have now aggregated the positions of millions of galaxies into three
dimensional density maps exposing a rich structure of clusters, filaments,
walls and voids.

However, redshift is not the only measure of radial distance. In particular,
dispersion of electromagnetic signals due to intervening plasma
is readily measured from fast radio bursts (FRB) which are a class
of radio transient first reported in \citet{lorimer}. The dispersion measure
(DM) is a line-of-site integral of the free electron density and can thus be
used as a distance estimate.
% IF COSMOLOGICAL!!

Neither redshift or dispersion measure are perfect proxies for radial distance.
Redshifts are systematically biased by the peculiar velocities of the object
relative to the Hubble flow. This leads to additional apparent clustering 
in redshift
space which was first calculated by \citet{kaiser} using linear theory.

Similarly, distance estimates from dispersion measure will be biased by
inhomogeneities in the electron density, again leading to additional apparent
clustering of sources in dispersion measure space.  In this letter we calculate
these DM space distortions and shaw that they could 
be usefully measured in a
survey detecting as few as 10\,000 fast radio bursts.

\section{Density perturbations in dispersion measure space}
The dispersion measure of a signal observed in some angular direction $\hat{n}$ and
originating from comoving radial distance $\chi$ is
\begin{equation}
    {\rm DM}(\hat{n}, \chi) = \int_0^{\chi} \ud\chi' a(\chi)^2
        n_e(\hat{n}\chi', \chi').
\end{equation}
Here
$n_e(\vec{x}, \chi)$ is the free electron density as a function of location and
conformal time. Note that we use $\chi$ as our radial distance and time
coordinate, as opposed to redshift which is more appropriate for spectroscopic
applications. We model the cosmological 
electron density as containing a homogeneous part
and perturbations
$n_e(\vec x, \chi) = \bar{n}_e(\chi) \left[1 + \delta_e(\vec x, \chi)\right]$.
The dispersion
measure is thus
\begin{equation}
    {\rm DM}(\hat n, \chi) = \int_0^\chi \ud\chi' a(\chi')^2 \bar{n}_e(\chi')
       \left[1 + \delta_e(\hat{n}\chi',\chi')\right].
\end{equation}

@@

\section{Two-point statistics}
Large-scale structure is usually studied through it two-point statistics, most
commonly the power-spectrum, $P(k)$.
Unlike in redshift-space distortions, Equation~\ref{e:delta_s} does not have a
simple form in harmonic space. The equation's third term couples harmonic modes
and thus the two-point statistics cannot be phrased as a simple power spectrum.
We will instead use $C^{ss}_\ell(\chi,\chi')$, which is
the cross-correlation angular power-spectrum of the DM space over-density
on shells at $\chi$ and $\chi'$.
\begin{align}
    &\delta_{\ell\ell'}\delta_{mm'}C^{ss}_\ell(\chi, \chi') = \nonumber \\
    & \quad
        \left\langle
        \int\ud\Omega Y_{\ell m}(\hat n)
       \delta_{fs}(\hat n \chi, \chi)
        \int\ud\Omega' Y_{\ell' m'}(\hat n')
        \delta_{fs}(\hat n' \chi', \chi')
        \right\rangle
\end{align}
The first two term in Equation~\ref{e:delta_s} are stationary. For stationary,
isotropic, tracers $x$ and $y$ we have 
$\langle \delta_x(\vec k, \chi) \delta_y(\vec k', \chi) \rangle = (2\pi)^3
\delta^3(\vec k - \vec k') P_{xy}(k, \chi)$.  If for a moment we ignore time
dependance, the angular cross power spectrum of such tracers is
\begin{align}
    %\delta_{\ell\ell'}\delta_{mm'}C^{xy}_\ell(\chi, \chi')
    %&= \int\ud\Omega\ud\Omega'Y_{\ell m}(\hat n) Y_{\ell' m'}(\hat n')
    %    \langle \delta_x(\hat n \chi) \delta_y(\hat n' \chi') \rangle,
    %    \\
    C^{xy}_\ell(\chi,\chi')
    &= \frac{2}{\pi}
\int_0^\infty\ud k k^2 j_\ell(k\chi) j_{\ell}(k\chi')P_{xy}(k).
\end{align}
In reality the power spectrum evolves on the order of a Hubble time.
The angular cross-correlations will be very small unless $\chi$ and $\chi'$ are
within a few correlation lengths of one another, roughly a few hundred
megaparsecs.  The evolution of the power-spectrum is negligible over these time
differences which leads to a straight forward way to include the evolution of
the perturbations:
\begin{align}
C^{xy}_\ell(\chi,\chi') 
    \approx \frac{2}{\pi}
    \int_0^\infty\ud k k^2
    j_\ell(k\chi) j_{\ell}(k\chi')
    P_{xy}(k,(\chi + \chi')/2),\nonumber &\\
    |\chi - \chi'| \ll 1/aH.&
\end{align}

@@

Equation~\ref{e:Clss} can be simplified substantially by adopting the small
angle and Limber approximations \citep{extened_limber}.  The small angle
approximation eliminates the $k$ integral over spherical Bessel functions, replacing it
with a Fourier transform, and is valid for $\ell \gg 1$. The Limber
approximation assumes that only modes with small radial component of their wave
vector contribute to the radial integrals and is valid if the power spectra
evolve slowly compared to the correlation length (which has already been
assumed). With these approximations we have
\begin{comment}
\begin{align}
C^{ss}_\ell(\chi, \chi') \approx&~
    \frac{1}{\bar\chi^2}
        \int_{-\infty}^\infty\frac{\ud k_\parallel}{(2 \pi)} 
        e^{i k_\parallel (\chi - \chi')}
        P_{[ee + ff - 2ef]}
        (\sqrt{k_\parallel^2 + \ell(\ell + 1)/\bar\chi^2}, \bar\chi)
        %\left[
        %P_{ee}(\sqrt{k_\parallel^2 + \ell^2/\bar\chi^2}, \bar\chi)
        %+ P_{ff}(\sqrt{k_\parallel^2 + \ell^2/\bar\chi^2}, \bar\chi)
        %- 2 P_{ef}(\sqrt{k_\parallel^2 + \ell^2/\bar\chi^2}, \bar\chi)
        %\right]
    \nonumber \\ &+
    %\left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi}
    %+ \frac{2}{\chi} \right)
    %\left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi'}
    %+ \frac{2}{\chi'} \right)
    A(\chi) A(\chi')
    \int_0^{\chi_{\rm min}}\ud\chi''
    \frac{1}{\chi^{\prime\prime 2}}
    P_{ee}((\ell + 1/2)/\chi'',\chi'')
    \nonumber \\ &+
    %\left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi_{\max}}
    %+ \frac{2}{\chi_{\max}} \right)
    \frac{A(\chi_{\max})}{\chi_{\min}^2}
    P_{[ee - ef]}((\ell + 1/2)/\chi_{\min}, \chi_{\min}),
        %\left[
        %    P_{ee}(\ell/\chi_{\min}, \chi_{\min})
        %    - P_{fe}(\ell/\chi_{\min}, \chi_{\min})
        %\right],
\end{align}
\end{comment}
\begin{align}
    &C^{ss}_\ell(\chi, \chi') \approx
    \nonumber \\ & \quad
    \frac{1}{\bar\chi^2}
        \int_{-\infty}^\infty\frac{\ud k_\parallel}{(2 \pi)} 
        e^{i k_\parallel (\chi - \chi')}
        P_{[ee + ff - 2ef]}
        (\sqrt{k_\parallel^2 + \nu^2/\bar\chi^2}, \bar\chi)
    \nonumber \\ & \quad +
    A(\chi) A(\chi')
    \int_0^{\chi_{\rm min}}\ud\chi''
    \frac{1}{\chi^{\prime\prime 2}}
    P_{ee}(\nu/\chi'',\chi'')
    \nonumber \\ & \quad +
    \frac{A(\chi_{\max})}{\chi_{\min}^2}
    P_{[ee - ef]}(\nu/\chi_{\min}, \chi_{\min}),
\end{align}
where $\nu\equiv\ell + 1/2$, $\chi_{\min} \equiv \min(\chi, \chi')$,
and $\chi_{\max} \equiv \max(\chi,
\chi')$ .  We've found that these approximations are excellent for $\ell
\gtrsim 10$
and use this form for the remainder of the paper.

\section{Modeling and measurement}
There are a number of effects that will complicate the measurement of the
above calculated angular power spectrum by a real survey of dispersion 
measures.  The first is
that the model that the free electron density decomposes into a homogeneous
part plus a random field of perturbations is not correct. Firstly, all signals
must pass through the Milky Way's galactic disk, halo and local environment
which will contribute to the dispersion measure. However, this is only a 
single function of $\hat n$  which can presumably be well
measured. In addition, this function could in principal be well characterized
by independent data such as observations of pulsars.  As such, the local
contribution is unlikely to be a limiting obstacle.

More concerning is the dispersion from the burst progenitor's environment
as well as the halo in which it resides.

@@

In this section we discuss some systematic effects that would affect a real
survey of dispersion measures, complicating measurement. We then estimate the
sensitivity of such a survey.

\subsection{Systematics}

DM contribution intrinsic to the source will have a few effects: There will be
an offset which will change the DM-distance relation in some way that can
hopefully be characterized. Also there will be a stochastic piece which will
smear out DM-distance relations and limit the effective width of the radial
shells. Detailed consideration of these effects is beyond the scope of this
work but to crudely deal with this, we don't consider any $\chi - \chi'$
smaller than \red{$100\,{\rm MPc}/h$}.

Contributions from local Universe probably not an issue. Can be measure by
other means and subtracted off.

Tomography is exact.  Get excellent separation of scales, unlike lensing.
The integral over $\chi$ couples many scales. In particular small scales (which
are difficult to model) will
be coupled to large angular scales by screens near the observer.  However
because tomography is exact, it would be possible to set up estimators that
decouple these scales, for instance by estimating the difference in power
between radial shells.  For this reason we start all radial integrals as
$\chi = 500\,{\rm MPc}/h$, which saves us from the difficulties in modelling the
small scale power.

\subsection{Detectability}

Here we present sensitivity estimates for a survey \ldots

We assume that the survey will be shot noise dominated as would be the case for
an initial detection.  The noise powerspectrum on a shells with of width
$\Delta \chi$ is
\begin{equation}
    C^N_{\ell, ij} = \frac{\delta_{ij}}{\bar n_f(\chi_i)\chi_i^2\Delta\chi},
\end{equation}
Here, to indicate that we are now working with quantities binned in the radial
direction instead of
continuous functions, we've switched to $C_{\ell,ij}$ over 
$C_\ell(\chi, \chi')$. The uncertainty on the angular
cross-power spectrum is then
\begin{align}
    (\Delta{C^{ss}_{\ell,ij}})^2 = 
    {\frac{1}{\ell(\ell + 1)\Delta \ell f_{\rm sky}}}
        \left[C^N_{\ell,ii} C^N_{\ell,jj} +  (C^N_{\ell,ij})^2\right],
\end{align}
where the second term in brackets only contributes for $i = j$.

To give an idea of the sensitivity of the survey, we collapse
$C^{ss}_{\ell,ij}$ to a single function of $\ell$ by taking a weighted average
of all pairs of radial bins. We use bin widths of $100\,{\rm MPc}/h$ over the
range $500\,{\rm MPc}/h$ to $3500\,{\rm MPc}/h$.
For weights in the radial bin average, we use the signal to uncertainty-squared
at $\ell=100$, which extracts all the signal to noise at that $\ell$ and much
of it at other multipoles.
We exclude the $i = j$ bin pairs due to
the presumed observational complications discussed in the previous section.
This effectively discards the contribution from the local term. This is shown
in Figure~\ref{f:sensitivity}.

>>>>

% Command to consume spaces and newlines.  Used to PRL style sections.
\makeatletter
\def\ignorespacesandimplicitepars{%
  \begingroup
  \catcode13=10
  \@ifnextchar\relax
    {\endgroup}%
    {\endgroup}%
}

\makeatletter

\renewcommand{\section}[1]{\emph{#1}---\ignorespacesandimplicitepars}
\renewcommand{\subsection}[1]{}

@@

    The recently discovered fast radio bursts are a new class of radio
    transient that, due to their high dispersion from intervening plasma,
    have been interpreted as
    originating from cosmological distances.  The rate of fast radio bursts
    has been estimated to be several thousand over the whole sky per day.  If
    cosmological, these events should trace the large-scale structure of the
    Universe in some way. Furthermore, because the dispersion measure (DM) can be
    used as a proxy for radial distance (like redshift),
    clustering can be studied in three dimensions. Due to inhomogeneities in
    the plasma's density dispersion measure is an imperfect proxy for radial
    distance and we show that this leads to additional clustering terms---the
    dispersion measure space distortions. We calculate the DM space
    power spectra for a toy model of electron and FRB clustering and show that
    the clustering signal could be detected in a survey of $10^4$ FRB
    events, as is expected to be produced by the Canadian Hydrogen Intensity
    Mapping Experiment.

@@

\section{Introduction}

The clustering of matter on large scales has been
heralded as the next great probe the Universe after the cosmic microwave
background (CMB). The large-scale structure in principle contains far more
information than the CMB, because it can be studied in three dimensions.
Traditionally the redshift of spectral lines caused by the Hubble flow has
been employed to measure radial distance. Such redshift
surveys have now aggregated the positions of millions of galaxies into three
dimensional density maps, exposing a rich structure of clusters, filaments,
walls and voids.

% This paragraph needs to be reorganized.
However, redshift is not the only measure of radial distance. In particular,
dispersion of electromagnetic signals due to intervening plasma
is readily measured from fast radio bursts (FRB) which are a class
of radio transient first reported in \citet{lorimer}. There have since been 
\ldots such bursts detected \citep{all_bursts} and total rate of bursts
been estimated to be \ldots. The dispersion measure
(DM) is a line-of-site integral of the free electron density and can thus be
used as a distance estimate.
If the progenitors of these bursts are at cosmological distances, with the
majority of the dispersion caused by electrons in the inter-galactic medium,
then the average DM-distance relation can be modelled \citep{someone}.

Neither redshift nor dispersion measure are perfect proxies for radial distance.
Redshifts are systematically biased by the peculiar velocities of the object
relative to the Hubble flow. This leads to additional apparent clustering 
in redshift
space which was first calculated by \citet{kaiser} using linear theory.
Similarly, distance estimates from dispersion measure will be biased by
inhomogeneities in the electron density, again leading to additional apparent
clustering of sources in dispersion measure space.  In this letter we calculate
these DM space distortions and consider the detectability of the signal by
upcoming surveys.

%\section{Density perturbations in dispersion measure space}
\section{Clustering in dispersion measure space}

The dispersion measure of a signal observed in some angular direction $\hat{n}$ and
originating from comoving radial distance $\chi$ is
\begin{equation}
    {\rm DM}(\hat{n}, \chi) = \int_0^{\chi} \ud\chi' a(\chi)^2
        n_e(\hat{n}\chi', \chi').
\end{equation}
Here
$n_e(\vec{x}, \chi)$ is the free electron density as a function of location and
conformal time. Note that we use $\chi$ as our radial distance and time
coordinate, as opposed to redshift which is more appropriate for spectroscopic
applications. We model the cosmological 
electron density as containing a homogeneous part
and perturbations
$n_e(\vec x, \chi) = \bar{n}_e(\chi) \left[1 + \delta_e(\vec x, \chi)\right]$.
The dispersion
measure is thus
\begin{equation}
    {\rm DM}(\hat n, \chi) = \int_0^\chi \ud\chi' a(\chi')^2 \bar{n}_e(\chi')
       \left[1 + \delta_e(\hat{n}\chi',\chi')\right].
\end{equation}

@@

%\section{Two-point statistics}

Large-scale structure is usually studied through it two-point statistics, most
commonly the power-spectrum, $P(k)$.
Unlike in redshift-space distortions, Equation~\ref{e:delta_s} does not have a
simple form in harmonic space. The equation's third term couples harmonic modes
and thus the two-point statistics cannot be phrased as a simple power spectrum.
We will instead use $C^{ss}_\ell(\chi,\chi')$, which is
the cross-correlation angular power-spectrum of the DM space over-density
on shells at $\chi$ and $\chi'$.
\begin{align}
    &\delta_{\ell\ell'}\delta_{mm'}C^{ss}_\ell(\chi, \chi') = \nonumber \\
    & \quad
        \left\langle
        \int\ud\Omega Y_{\ell m}(\hat n)
       \delta_{fs}(\hat n \chi, \chi)
        \int\ud\Omega' Y_{\ell' m'}(\hat n')
        \delta_{fs}(\hat n' \chi', \chi')
        \right\rangle
\end{align}
The first two term in Equation~\ref{e:delta_s} are stationary. For stationary,
isotropic, tracers $x$ and $y$ we have 
$\langle \delta_x(\vec k, \chi) \delta_y(\vec k', \chi) \rangle = (2\pi)^3
\delta^3(\vec k - \vec k') P_{xy}(k, \chi)$.  If for a moment we ignore time
dependance, the angular cross power spectrum of such tracers is
\begin{align}
    %\delta_{\ell\ell'}\delta_{mm'}C^{xy}_\ell(\chi, \chi')
    %&= \int\ud\Omega\ud\Omega'Y_{\ell m}(\hat n) Y_{\ell' m'}(\hat n')
    %    \langle \delta_x(\hat n \chi) \delta_y(\hat n' \chi') \rangle,
    %    \\
    C^{xy}_\ell(\chi,\chi')
    &= \frac{2}{\pi}
\int_0^\infty\ud k k^2 j_\ell(k\chi) j_{\ell}(k\chi')P_{xy}(k).
\end{align}
In reality the power spectrum evolves on the order of a Hubble time.
The angular cross-correlations will be very small unless $\chi$ and $\chi'$ are
within a few correlation lengths of one another, roughly a few hundred
megaparsecs.  The evolution of the power-spectrum is negligible over these time
differences which leads to a straight forward way to include the evolution of
the perturbations:
\begin{align}
C^{xy}_\ell(\chi,\chi') 
    \approx \frac{2}{\pi}
    \int_0^\infty\ud k k^2
    j_\ell(k\chi) j_{\ell}(k\chi')
    P_{xy}(k,(\chi + \chi')/2),\nonumber &\\
    |\chi - \chi'| \ll 1/aH.&
\end{align}

@@

Equation~\ref{e:Clss} can be simplified substantially by adopting the small
angle and Limber approximations \citep{extened_limber}.  The small angle
approximation eliminates the $k$ integral over spherical Bessel functions, replacing it
with a Fourier transform, and is valid for $\ell \gg 1$. The Limber
approximation assumes that only modes with small radial component of their wave
vector contribute to the radial integrals and is valid if the power spectra
evolve slowly compared to the correlation length (which has already been
assumed). With these approximations we have
\begin{align}
    &C^{ss}_\ell(\chi, \chi') \approx
    \nonumber \\ & \quad
    \frac{1}{\bar\chi^2}
        \int_{-\infty}^\infty\frac{\ud k_\parallel}{(2 \pi)} 
        e^{i k_\parallel (\chi - \chi')}
        P_{[ee + ff - 2ef]}
        (\sqrt{k_\parallel^2 + \nu^2/\bar\chi^2}, \bar\chi)
    \nonumber \\ & \quad +
    A(\chi) A(\chi')
    \int_0^{\chi_{\rm min}}\ud\chi''
    \frac{1}{\chi^{\prime\prime 2}}
    P_{ee}(\nu/\chi'',\chi'')
    \nonumber \\ & \quad +
    \frac{A(\chi_{\max})}{\chi_{\min}^2}
    P_{[ee - ef]}(\nu/\chi_{\min}, \chi_{\min}),
    \label{e:Clss_limber}
\end{align}
where $\nu\equiv\ell + 1/2$, $\chi_{\min} \equiv \min(\chi, \chi')$,
and $\chi_{\max} \equiv \max(\chi,
\chi')$ .  We've found that these approximations are excellent for $\ell
\gtrsim 10$
and use this form for the remainder of the paper.

\section{Modeling and measurement}

There are a number of effects that will complicate the measurement of the
above calculated angular power spectrum by a real survey of dispersion 
measures.  The first is
that the model that the free electron density decomposes into a homogeneous
part plus a random field of perturbations is not correct. Firstly, all signals
must pass through the Milky Way's galactic disk, halo and local environment
which will contribute to the dispersion measure. However, this is only a 
single function of $\hat n$  which can presumably be well
measured. In addition, this function could in principal be well characterized
by independent data such as observations of pulsars.  As such, the local
contribution is unlikely to be a limiting obstacle. \red{cite geansler paper?}

More concerning is the dispersion from the burst progenitor's environment
as well as the halo in which it resides. These electrons will presumably be
clustered around the burst progenitor on scales far smaller than DM space
structure maps and thus are not accounted for in the $\delta_e$--$\delta_f$
correlations included in the above formalism.  This will have a mean
contribution, common to all bursts and which may be epoch dependant, which will
modify the mean DM--distance relation. This will need to be calibrated in some
why or else fit with nuisance parameters during parameter estimation.  There
will also be a stochastic piece which varies from burst to burst.  This will
limit the precision at which $\chi_s$ can be measured, thus limiting the
resolution of DM space density maps in the radial direction.

Detailed treatment of these complications is beyond the scope of the current
work. The magnitude of the contribution from the progenitor is at present
unconstrained by data. To crudely deal with it here we use relatively large 
$\chi$ bins of $100\,{\rm MPc}/h$ in sensitivity estimates.

The second term in Equation~\ref{e:Clss_limber} is an integral that mixes
many spacial scales, small scales from smaller radial distance and larger
scales from greater distances. The mixing of scales complicates the
interpretation of measurements, since structure formation on scales smaller
than $\sim10\,{\rm MPc}/h$ is non-linear and hard to model. A similar issue
exists in the field of weak gravitational lensing, where the formula for the
angular power spectrum has a similar form.  However in lensing a kernel in
the line-of-sight integral, arising from geometric effects, suppresses the
contribution from small distances, partially alleviating the issue.

There is an advantage to the lack of kernel in the DM space integral term.
Lensing tomography---the use of sources at multiple redshifts to unmix
spatial scales---is complicated by the kernel. The kernel's shape depends on
the source redshift, reweighting the line of sight and
making tomography inexact.  In contrast the integrand in the integral
term is completely independent of the limit of integration, meaning
contributions from different parts of the line of sight (and thus different
spatial scales) can be separated exactly. Again, a detailed study of DM space
tomography is beyond the scope of this work.  The avoid our results being
sensitive to the hard-to-model small scales, we assume that the contribution to the
integral term from radial distances $\chi'' < 500\,{\rm MPc}/h$ are well
measured by the correlations with these radial slices. We thus neglect the
information from these slices in our sensitivity measurements and ignore
contributions to the integral term from below this distance. The smallest
spatial scale that contributes the our plotted angular power spectra out to
$\ell=1000$ is thus $k=2\,h/{\rm MPc}$.

@@

In first measurements of the angular power spectra, uncertainty will be
dominated by the finite number of observed dispersion measures, or shot noise.
The noise power spectrum on a shells with of width
$\Delta \chi$ is
\begin{equation}
    C^N_{\ell, ij} = \frac{\delta_{ij}}{\bar n_f(\chi_i)\chi_i^2\Delta\chi},
\end{equation}
Here, to indicate that we are now working with quantities binned in the radial
direction instead of
continuous functions, we've switched to $C_{\ell,ij}$ over 
$C_\ell(\chi, \chi')$. The uncertainty on the angular
cross-power spectrum is then
\begin{align}
    (\Delta{C^{ss}_{\ell,ij}})^2 = 
    {\frac{1}{\ell(\ell + 1)\Delta \ell f_{\rm sky}}}
        \left[C^N_{\ell,ii} C^N_{\ell,jj} +  (C^N_{\ell,ij})^2\right],
\end{align}
where the second term in brackets only contributes for $i = j$.

Here we consider the sensitivity of a survey with a total of $10^4$ dispersion
measures from FRBs distributed uniformly over half the sky. This is in rough
approximation to what could be achieved by the Canadian Hydrogen Intensity
Mapping Experiment's now funded FRB instrument over a three year survey
\citep{who}.
To give an idea of the overall sensitivity of the survey, we collapse
$C^{ss}_{\ell,ij}$ to a single function of $\ell$ by taking a weighted average
of all pairs of radial bins. We use bin widths of $100\,{\rm MPc}/h$ over the
range $500\,{\rm MPc}/h$ to $3500\,{\rm MPc}/h$.
For weights in the radial bin average, we use the signal to noise-squared
at $\ell=100$, which maximizes the signal to noise at that $\ell$ and
is near optimal at other multipoles.
We exclude the $i = j$ bin pairs
as they would be contaminated by noise bias in a real survey.
This effectively discards the contribution from the local term. The result is shown
in Figure~\ref{f:sensitivity}.
